Reading main files and preparing data sets

### 2024-12-11 data-raw/03-preprocessing-main-files.Rmd
Documentation for main GSS files

```{r SURVMNTH}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SURVMNTH: Survey month of data collection from April 2015 to March 2016
    SURVMNTH = 
           case_when(SURVMNTH == 1 ~ "January", 
                     SURVMNTH == 2 ~ "February",
                     SURVMNTH == 3 ~ "March",
                     SURVMNTH == 4 ~ "April",
                     SURVMNTH == 5 ~ "May",
                     SURVMNTH == 6  ~ "June",
                     SURVMNTH == 7 ~ "July",
                     SURVMNTH == 8 ~ "August",
                     SURVMNTH == 9 ~ "September",
                     SURVMNTH == 10 ~ "October",
                     SURVMNTH == 11 ~ "November",
                     SURVMNTH == 12 ~ "December",
                     SURVMNTH == 96 ~ "Valid skip",
                     SURVMNTH == 97 ~ "Don't know",
                     SURVMNTH == 98 ~ "Refusal",
                     SURVMNTH == 99 ~ "Not stated"), 
    SURVMNTH = factor(SURVMNTH))

@@

```{r AGEGR10}
values_ordered <- c("15 to 24 years","25 to 34 years","35 to 44 years",
                    "45 to 54 years", "55 to 64 years","65 to 74 years","75 years and over")

@@

```{r MARSTAT}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # MARSTAT: Marital status of the respondent
    MARSTAT = 
           case_when(MARSTAT == 1 ~ "Married", 
                     MARSTAT == 2 ~ "Living common-law",
                     MARSTAT == 3 ~ "Widowed",
                     MARSTAT == 4 ~ "Separated",
                     MARSTAT == 5 ~ "Divorced",
                     MARSTAT == 6  ~ "Single, never married",
                     MARSTAT == 96 ~ "Valid skip",
                     MARSTAT == 97 ~ "Don't know",
                     MARSTAT == 98 ~ "Refusal",
                     MARSTAT == 99 ~ "Not stated"), 
    MARSTAT = factor(MARSTAT))

@@

```{r AGEPRGRD}
values_ordered <- c("Respondent is 11 + years older", 
                    "Respondent is 6 - 10 years older",
                    "Respondent is 5 years older",
                    "Respondent is 4 years older",
                    "Respondent is 3 years older",
                    "Respondent is 2 years older",
                    "Respondent is 1 years older",
                    "Respondent and spouse/partner are the same age",
                    "Respondent is 1 years younger",
                    "Respondent is 2 years younger",
                    "Respondent is 3 years younger",
                    "Respondent is 4 years younger",
                    "Respondent is 5 years younger",
                    "Respondent is 6 - 10 years younger",
                    "Respondent is 11 + years younger",
                    "Valid skip")

@@

```{r SEXPR}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SEXPR: Sex of respondent's spouse/partner living in the household.
    SEXPR = 
           case_when(SEXPR == 1 ~ "Male spouse/partner in the household", 
                     SEXPR == 2 ~ "Female spouse/partner in the household",
                     SEXPR == 6 ~ "Valid skip",
                     SEXPR == 7 ~ "Don't know",
                     SEXPR == 8 ~ "Refusal",
                     SEXPR == 9 ~ "Not stated"), 
    SEXPR = factor(SEXPR))

@@

```{r PRTYPEC}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PRTYPEC: Type of partner respondent has living in the household.
    PRTYPEC = 
           case_when(PRTYPEC == 1 ~ "Opposite sex married partner in the household", 
                     PRTYPEC == 2 ~ "Opposite sex common-law partner in the household",
                     PRTYPEC == 3 ~ "Same sex married or common-law partner in the household",
                     PRTYPEC == 6 ~ "Valid skip",
                     PRTYPEC == 7 ~ "Don't know",
                     PRTYPEC == 8 ~ "Refusal",
                     PRTYPEC == 9 ~ "Not stated"), 
    PRTYPEC = factor(PRTYPEC))

@@

```{r CXRFLAG}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # CXRFLAG:  Child(ren) of the respondent living in the household.
    CXRFLAG = 
           case_when(CXRFLAG == 1 ~ "Yes", 
                     CXRFLAG == 2 ~ "No",
                     CXRFLAG == 6 ~ "Valid skip",
                     CXRFLAG == 7 ~ "Don't know",
                     CXRFLAG == 8 ~ "Refusal",
                     CXRFLAG == 9 ~ "Not stated"), 
    CXRFLAG = factor(CXRFLAG))

@@

```{r AGECXRYG}
values_ordered <- c( "Valid skip", "5 to 4", "5 to 9","10 to 14",
                     "15 to 19","20 to 24",
                     "25 years and older")

@@

```{r CHINHSDC}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three",
                     "Four or more")

@@

```{r CXR0014C}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three or more")

@@

```{r CHH0014C}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three or more")

@@

```{r CXRTIME6}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # CXRTIME6:  Age group of respondent’s child(ren) in household
    CXRTIME6 = 
           case_when(CXRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CXRTIME6 == 2 ~ "All children under 5 years of age",
                     CXRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CXRTIME6 == 4 ~ "All children 13 years of age and older",
                     CXRTIME6 == 5 ~ "At least one child under 5 years of age but not all
children",
                     CXRTIME6 == 6 ~ "Other",
                     CXRTIME6 == 96 ~ "Valid skip",
                     CXRTIME6 == 97 ~ "Don't know",
                     CXRTIME6 == 98 ~ "Refusal",
                     CXRTIME6 == 99 ~ "Not stated"), 
    CXRTIME6 = factor(CXRTIME6))

@@

```{r PARNUM}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PARNUM: Number of parents the respondent has in household
    PARNUM = 
           case_when(PARNUM == 0 ~ "None",
                     PARNUM == 1 ~ "One parent",
                     PARNUM == 2 ~ "Two parents",
                     PARNUM == 6 ~ "Valid skip",
                     PARNUM == 7 ~ "Don't know",
                     PARNUM == 8 ~ "Refusal",
                     PARNUM == 9 ~ "Not stated"), 
    PARNUM = factor(PARNUM))

@@

```{r LIVARR08}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LIVARR08: Living arrangement of respondent’s household (8 categories)
    LIVARR08 = 
           case_when(LIVARR08 == 1 ~ "Under 25 years - Not living with parents",
                     LIVARR08 == 2 ~ "Under 25 years - Living with both parents",
                     LIVARR08 == 3 ~ "Under 25 years - Living with mother only",
                     LIVARR08 == 4 ~ "Under 25 years - Living with father only",
                     LIVARR08 == 5 ~ "25 years of age or older - Not living with parents",
                     LIVARR08 == 6 ~ "25 years of age or older - Living with both parents",
                     LIVARR08 == 7 ~ "25 years of age or older - Living with mother only",
                     LIVARR08 == 8 ~ "25 years of age or older - Living with father only",
                     LIVARR08 == 96 ~ "Valid skip",
                     LIVARR08 == 97 ~ "Don't know",
                     LIVARR08 == 98 ~ "Refusal",
                     LIVARR08 == 99 ~ "Not stated"), 
    LIVARR08 = factor(LIVARR08))

@@

```{r LIVARR11} 
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LIVARR11: Living arrangement of respondent’s household (11 categories)
    LIVARR11 = 
           case_when(LIVARR11 == 1 ~ "Living alone",
                     LIVARR11 == 2 ~ "Living with sponse only",
                     LIVARR11 == 3 ~ "Living with spouse and child(ren) < 25 years",
                     LIVARR11 == 4 ~ "Living with spouse and child(ren) 25 years or older",
                     LIVARR11 == 5 ~ "Living with spouse and other",
                     LIVARR11 == 6 ~ "Living without spouse but with chil(ren) < 25 years",
                     LIVARR11 == 7 ~ "Living without spouse but with chil(ren) 25 years and older",
                     LIVARR11 == 8 ~ "Living with two parents",
                     LIVARR11 == 9 ~ "Living with one parent",
                     LIVARR11 == 10 ~ "Multiple person household - Other living arrangement",
                     LIVARR11 == 11 ~ "Multiple person household - Relationships undefined",
                     LIVARR11 == 96 ~ "Valid skip",
                     LIVARR11 == 97 ~ "Don't know",
                     LIVARR11 == 98 ~ "Refusal",
                     LIVARR11 == 99 ~ "Not stated"), 
    LIVARR11 = factor(LIVARR11))

@@

```{r HSDSIZEC}
values_ordered <- c("One person household",
                   "Two person household",
                   "Three person household",
                   "Four person household",
                   "Five person household",
                   "Six or more person household")

@@

```{r HSDELIGC}
values_ordered <- c("One member",
                     "Two members",
                     "Three members",
                     "Four or more members")

@@

```{r MULTIGEN}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # MULTIGEN:  Three generations or more in the respondent’s household
    MULTIGEN = 
           case_when(MULTIGEN == 1 ~ "Yes", 
                     MULTIGEN == 2 ~ "No",
                     MULTIGEN == 6 ~ "Valid skip",
                     MULTIGEN == 7 ~ "Don't know",
                     MULTIGEN == 8 ~ "Refusal",
                     MULTIGEN == 9 ~ "Not stated"), 
    MULTIGEN = factor(MULTIGEN))

@@

```{r PRV}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PRV: Province of residence
    PRV = 
      case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia",
                     PRV == 96 ~ "Valid skip",
                     PRV == 97 ~ "Don't know",
                     PRV == 98 ~ "Refusal",
                     PRV == 99 ~ "Not stated"),
    PRV = factor(PRV))

@@

```{r LUC_RST}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LUC_RST:  Population centre indicator
    LUC_RST = 
      case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "Prince Edward Island",
                     LUC_RST == 6 ~ "Valid skip",
                     LUC_RST == 7 ~ "Don't know",
                     LUC_RST == 8 ~ "Refusal",
                     LUC_RST == 9 ~ "Not stated"),
    LUC_RST = factor(LUC_RST))

@@

```{r GTU_110}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r GTU_130}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r DVTDAY}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # DVTDAY: Diary - Reference day - Type
    DVTDAY = 
      case_when(DVTDAY == 1 ~ "Weekday",
                     DVTDAY == 2 ~ "Saturday",
                     DVTDAY == 3 ~ "Sunday",
                     DVTDAY == 96 ~ "Valid skip",
                     DVTDAY == 97 ~ "Don't know",
                     DVTDAY == 98 ~ "Refusal",
                     DVTDAY == 99 ~ "Not stated"),
    DVTDAY = factor(DVTDAY))

@@

Save data in R format for later use:
```{r}
usethis::use_data(gss_main_2015, 
                  overwrite = TRUE)
```

@@

```{r MARSTAT}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # MARSTAT: Marital status of the respondent
    MARSTAT = 
           case_when(MARSTAT == 1 ~ "Married", 
                     MARSTAT == 2 ~ "Living common-law",
                     MARSTAT == 3 ~ "Widowed",
                     MARSTAT == 4 ~ "Separated",
                     MARSTAT == 5 ~ "Divorced",
                     MARSTAT == 6  ~ "Single, never married",
                     MARSTAT == 8 ~ "Don't know",
                     MARSTAT == 9 ~ "Not stated"), 
    MARSTAT = factor(MARSTAT))

@@

```{r AGECHRYC}

@@

```{r PARHSDC}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # PARHSDC: Type of parents the respondent has within the household.
    PARHSDC = 
           case_when(PARHSDC == 1 ~ "Two biological parents",
                     PARHSDC == 2 ~ "Two parents (biological/adoptive/step)",
                     PARHSDC == 3 ~ "Only one parent",
                     PARHSDC == 7 ~ "Not asked - no parents in the household"), 
    PARHSDC = factor(PARHSDC))

@@

```{r LIVARR08}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # LIVARR08: Living arrangement of respondent’s household (8 categories)
    LIVARR08 = 
           case_when(LIVARR08 == 1 ~ "Under 25 years - Not living with parents",
                     LIVARR08 == 2 ~ "Under 25 years - Living with both parents",
                     LIVARR08 == 3 ~ "Under 25 years - Living with mother only",
                     LIVARR08 == 4 ~ "Under 25 years - Living with father only",
                     LIVARR08 == 5 ~ "25 years of age or older - Not living with parents",
                     LIVARR08 == 6 ~ "25 years of age or older - Living with both parents",
                     LIVARR08 == 7 ~ "25 years of age or older - Living with mother only",
                     LIVARR08 == 8 ~ "25 years of age or older - Living with father only"), 
    LIVARR08 = factor(LIVARR08))

@@

```{r HSDSIZEC}
values_ordered <- c("One person household",
                   "Two person household",
                   "Three person household",
                   "Four person household",
                   "Five person household",
                   "Six or more person household")

@@

```{r HSDELIGC}
values_ordered <- c("One member",
                     "Two members",
                     "Three members",
                     "Four members", "Five household members or more")

@@

summary(gss_main_2010$HSDELIGC)
```
```{r FAMTYPE-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # FAMTYPE: Respondent's type of family structure.
    FAMTYPE = 
           case_when(FAMTYPE == 1 ~ "Couple only", 
                     FAMTYPE == 2 ~ "Intact family",
                     FAMTYPE == 3 ~ "Step family with common child",
                     FAMTYPE == 4 ~ "Step family without a common child",
                     FAMTYPE == 5 ~ "Lone parent family",
                     FAMTYPE == 7 ~ "No spouse/partner or children in household"), 
    FAMTYPE = factor(FAMTYPE))

@@

```{r MULTIGEN}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # MULTIGEN:  Three generations or more in the respondent’s household
    MULTIGEN = 
           case_when(MULTIGEN == 1 ~ "Yes", 
                     MULTIGEN == 2 ~ "No",
                     MULTIGEN == 6 ~ "Number of generations unknown"), 
    MULTIGEN = factor(MULTIGEN))

@@

summary(gss_main_2010$PRV) 
```
```{r REGION-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # REGION:  Region of residence of the respondent.
    REGION = 
      case_when(REGION == 1 ~ "Atlantic region",
                     REGION == 2 ~ "Quebec",
                     REGION == 3 ~ "Ontario",
                     REGION == 4 ~ "Prairie region",
                     REGION == 5 ~ "British Columbia"),
    REGION = factor(REGION))

@@

```{r LUC_RST}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # LUC_RST:  Population centre indicator
    LUC_RST = 
      case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "Prince Edward Island"),
    LUC_RST = factor(LUC_RST))

@@

```{r GTU_110}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r GTU_130}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r DVTDAY}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # DVTDAY: Diary - Reference day - Type
    DVTDAY = 
      case_when(DVTDAY == 1 ~ "Weekday",
                     DVTDAY == 2 ~ "Saturday",
                     DVTDAY == 3 ~ "Sunday"),
    DVTDAY = factor(DVTDAY))

@@

Save data in R format for later use:
```{r}
usethis::use_data(gss_main_2010, 
                  overwrite = TRUE)
```

@@

```{r filtering-variables-2010}
gss_main_2005 <- gss_m_2005 %>%
  select(RECID:DVTDAY)
```

@@

@@

>>>>

```{r SURVMNTH-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SURVMNTH: Survey month of data collection from April 2015 to March 2016
    SURVMNTH = 
           case_when(SURVMNTH == 1 ~ "January", 
                     SURVMNTH == 2 ~ "February",
                     SURVMNTH == 3 ~ "March",
                     SURVMNTH == 4 ~ "April",
                     SURVMNTH == 5 ~ "May",
                     SURVMNTH == 6  ~ "June",
                     SURVMNTH == 7 ~ "July",
                     SURVMNTH == 8 ~ "August",
                     SURVMNTH == 9 ~ "September",
                     SURVMNTH == 10 ~ "October",
                     SURVMNTH == 11 ~ "November",
                     SURVMNTH == 12 ~ "December",
                     SURVMNTH == 96 ~ "Valid skip",
                     SURVMNTH == 97 ~ "Don't know",
                     SURVMNTH == 98 ~ "Refusal",
                     SURVMNTH == 99 ~ "Not stated"), 
    SURVMNTH = factor(SURVMNTH))

@@

```{r AGEGR10-2015}
values_ordered <- c("15 to 24 years","25 to 34 years","35 to 44 years",
                    "45 to 54 years", "55 to 64 years","65 to 74 years","75 years and over")

@@

```{r MARSTAT-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # MARSTAT: Marital status of the respondent
    MARSTAT = 
           case_when(MARSTAT == 1 ~ "Married", 
                     MARSTAT == 2 ~ "Living common-law",
                     MARSTAT == 3 ~ "Widowed",
                     MARSTAT == 4 ~ "Separated",
                     MARSTAT == 5 ~ "Divorced",
                     MARSTAT == 6  ~ "Single, never married",
                     MARSTAT == 96 ~ "Valid skip",
                     MARSTAT == 97 ~ "Don't know",
                     MARSTAT == 98 ~ "Refusal",
                     MARSTAT == 99 ~ "Not stated"), 
    MARSTAT = factor(MARSTAT))

@@

```{r AGEPRGRD-2015}
values_ordered <- c("Respondent is 11 + years older", 
                    "Respondent is 6 - 10 years older",
                    "Respondent is 5 years older",
                    "Respondent is 4 years older",
                    "Respondent is 3 years older",
                    "Respondent is 2 years older",
                    "Respondent is 1 years older",
                    "Respondent and spouse/partner are the same age",
                    "Respondent is 1 years younger",
                    "Respondent is 2 years younger",
                    "Respondent is 3 years younger",
                    "Respondent is 4 years younger",
                    "Respondent is 5 years younger",
                    "Respondent is 6 - 10 years younger",
                    "Respondent is 11 + years younger",
                    "Valid skip")

@@

```{r SEXPR-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SEXPR: Sex of respondent's spouse/partner living in the household.
    SEXPR = 
           case_when(SEXPR == 1 ~ "Male spouse/partner in the household", 
                     SEXPR == 2 ~ "Female spouse/partner in the household",
                     SEXPR == 6 ~ "Valid skip",
                     SEXPR == 7 ~ "Don't know",
                     SEXPR == 8 ~ "Refusal",
                     SEXPR == 9 ~ "Not stated"), 
    SEXPR = factor(SEXPR))

@@

```{r PRTYPEC-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PRTYPEC: Type of partner respondent has living in the household.
    PRTYPEC = 
           case_when(PRTYPEC == 1 ~ "Opposite sex married partner in the household", 
                     PRTYPEC == 2 ~ "Opposite sex common-law partner in the household",
                     PRTYPEC == 3 ~ "Same sex married or common-law partner in the household",
                     PRTYPEC == 6 ~ "Valid skip",
                     PRTYPEC == 7 ~ "Don't know",
                     PRTYPEC == 8 ~ "Refusal",
                     PRTYPEC == 9 ~ "Not stated"), 
    PRTYPEC = factor(PRTYPEC))

@@

```{r CXRFLAG-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # CXRFLAG:  Child(ren) of the respondent living in the household.
    CXRFLAG = 
           case_when(CXRFLAG == 1 ~ "Yes", 
                     CXRFLAG == 2 ~ "No",
                     CXRFLAG == 6 ~ "Valid skip",
                     CXRFLAG == 7 ~ "Don't know",
                     CXRFLAG == 8 ~ "Refusal",
                     CXRFLAG == 9 ~ "Not stated"), 
    CXRFLAG = factor(CXRFLAG))

@@

```{r AGECXRYG-2015}
values_ordered <- c( "Valid skip", "5 to 4", "5 to 9","10 to 14",
                     "15 to 19","20 to 24",
                     "25 years and older")

@@

```{r CHINHSDC-2015}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three",
                     "Four or more")

@@

```{r CXR0014C-2015}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three or more")

@@

```{r CHH0014C-2015}
values_ordered <- c("None", 
                     "One",
                     "Two",
                     "Three or more")

@@

```{r CXRTIME6-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # CXRTIME6:  Age group of respondent’s child(ren) in household
    CXRTIME6 = 
           case_when(CXRTIME6 == 1 ~ "No child under 19 years of age at home",
                     CXRTIME6 == 2 ~ "All children under 5 years of age",
                     CXRTIME6 == 3 ~ "All children between 5 and 12 years of age",
                     CXRTIME6 == 4 ~ "All children 13 years of age and older",
                     CXRTIME6 == 5 ~ "At least one child under 5 years of age but not all
children",
                     CXRTIME6 == 6 ~ "Other",
                     CXRTIME6 == 96 ~ "Valid skip",
                     CXRTIME6 == 97 ~ "Don't know",
                     CXRTIME6 == 98 ~ "Refusal",
                     CXRTIME6 == 99 ~ "Not stated"), 
    CXRTIME6 = factor(CXRTIME6))

@@

```{r PARNUM-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PARNUM: Number of parents the respondent has in household
    PARNUM = 
           case_when(PARNUM == 0 ~ "None",
                     PARNUM == 1 ~ "One parent",
                     PARNUM == 2 ~ "Two parents",
                     PARNUM == 6 ~ "Valid skip",
                     PARNUM == 7 ~ "Don't know",
                     PARNUM == 8 ~ "Refusal",
                     PARNUM == 9 ~ "Not stated"), 
    PARNUM = factor(PARNUM))

@@

```{r LIVARR08-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LIVARR08: Living arrangement of respondent’s household (8 categories)
    LIVARR08 = 
           case_when(LIVARR08 == 1 ~ "Under 25 years - Not living with parents",
                     LIVARR08 == 2 ~ "Under 25 years - Living with both parents",
                     LIVARR08 == 3 ~ "Under 25 years - Living with mother only",
                     LIVARR08 == 4 ~ "Under 25 years - Living with father only",
                     LIVARR08 == 5 ~ "25 years of age or older - Not living with parents",
                     LIVARR08 == 6 ~ "25 years of age or older - Living with both parents",
                     LIVARR08 == 7 ~ "25 years of age or older - Living with mother only",
                     LIVARR08 == 8 ~ "25 years of age or older - Living with father only",
                     LIVARR08 == 96 ~ "Valid skip",
                     LIVARR08 == 97 ~ "Don't know",
                     LIVARR08 == 98 ~ "Refusal",
                     LIVARR08 == 99 ~ "Not stated"), 
    LIVARR08 = factor(LIVARR08))

@@

```{r LIVARR11-2015} 
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LIVARR11: Living arrangement of respondent’s household (11 categories)
    LIVARR11 = 
           case_when(LIVARR11 == 1 ~ "Living alone",
                     LIVARR11 == 2 ~ "Living with sponse only",
                     LIVARR11 == 3 ~ "Living with spouse and child(ren) < 25 years",
                     LIVARR11 == 4 ~ "Living with spouse and child(ren) 25 years or older",
                     LIVARR11 == 5 ~ "Living with spouse and other",
                     LIVARR11 == 6 ~ "Living without spouse but with chil(ren) < 25 years",
                     LIVARR11 == 7 ~ "Living without spouse but with chil(ren) 25 years and older",
                     LIVARR11 == 8 ~ "Living with two parents",
                     LIVARR11 == 9 ~ "Living with one parent",
                     LIVARR11 == 10 ~ "Multiple person household - Other living arrangement",
                     LIVARR11 == 11 ~ "Multiple person household - Relationships undefined",
                     LIVARR11 == 96 ~ "Valid skip",
                     LIVARR11 == 97 ~ "Don't know",
                     LIVARR11 == 98 ~ "Refusal",
                     LIVARR11 == 99 ~ "Not stated"), 
    LIVARR11 = factor(LIVARR11))

@@

```{r HSDSIZEC-2015}
values_ordered <- c("One person household",
                   "Two person household",
                   "Three person household",
                   "Four person household",
                   "Five person household",
                   "Six or more person household")

@@

```{r HSDELIGC-2015}
values_ordered <- c("One member",
                     "Two members",
                     "Three members",
                     "Four or more members")

@@

```{r MULTIGEN-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # MULTIGEN:  Three generations or more in the respondent’s household
    MULTIGEN = 
           case_when(MULTIGEN == 1 ~ "Yes", 
                     MULTIGEN == 2 ~ "No",
                     MULTIGEN == 6 ~ "Valid skip",
                     MULTIGEN == 7 ~ "Don't know",
                     MULTIGEN == 8 ~ "Refusal",
                     MULTIGEN == 9 ~ "Not stated"), 
    MULTIGEN = factor(MULTIGEN))

@@

```{r PRV-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # PRV: Province of residence
    PRV = 
      case_when(PRV == 10 ~ "Newfoundland and Labrador",
                     PRV == 11 ~ "Prince Edward Island",
                     PRV == 12 ~ "Nova Scotia",
                     PRV == 13 ~ "New Brunswick",
                     PRV == 24 ~ "Quebec",
                     PRV == 35 ~ "Ontario",
                     PRV == 46 ~ "Manitoba",
                     PRV == 47 ~ "Saskatchewan",
                     PRV == 48 ~ "Alberta",
                     PRV == 59 ~ "British Columbia",
                     PRV == 96 ~ "Valid skip",
                     PRV == 97 ~ "Don't know",
                     PRV == 98 ~ "Refusal",
                     PRV == 99 ~ "Not stated"),
    PRV = factor(PRV))

@@

```{r LUC_RST-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # LUC_RST:  Population centre indicator
    LUC_RST = 
      case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "Prince Edward Island",
                     LUC_RST == 6 ~ "Valid skip",
                     LUC_RST == 7 ~ "Don't know",
                     LUC_RST == 8 ~ "Refusal",
                     LUC_RST == 9 ~ "Not stated"),
    LUC_RST = factor(LUC_RST))

@@

```{r GTU_110-2015}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r GTU_130-2015}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r DVTDAY-2015}
gss_main_2015 <- gss_main_2015 %>% 
  mutate( # DVTDAY: Diary - Reference day - Type
    DVTDAY = 
      case_when(DVTDAY == 1 ~ "Weekday",
                     DVTDAY == 2 ~ "Saturday",
                     DVTDAY == 3 ~ "Sunday",
                     DVTDAY == 96 ~ "Valid skip",
                     DVTDAY == 97 ~ "Don't know",
                     DVTDAY == 98 ~ "Refusal",
                     DVTDAY == 99 ~ "Not stated"),
    DVTDAY = factor(DVTDAY))

@@

Save data in R format for later use:
```{r save-data-2015}
usethis::use_data(gss_main_2015, 
                  overwrite = TRUE)
```

@@

```{r MARSTAT-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # MARSTAT: Marital status of the respondent
    MARSTAT = 
           case_when(MARSTAT == 1 ~ "Married", 
                     MARSTAT == 2 ~ "Living common-law",
                     MARSTAT == 3 ~ "Widowed",
                     MARSTAT == 4 ~ "Separated",
                     MARSTAT == 5 ~ "Divorced",
                     MARSTAT == 6  ~ "Single, never married",
                     MARSTAT == 8 ~ "Don't know",
                     MARSTAT == 9 ~ "Not stated"), 
    MARSTAT = factor(MARSTAT))

@@

```{r AGECHRYC-2010}

@@

```{r PARHSDC-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # PARHSDC: Type of parents the respondent has within the household.
    PARHSDC = 
           case_when(PARHSDC == 1 ~ "Two biological parents",
                     PARHSDC == 2 ~ "Two parents (biological/adoptive/step)",
                     PARHSDC == 3 ~ "Only one parent",
                     PARHSDC == 7 ~ "Not asked - no parents in the household"), 
    PARHSDC = factor(PARHSDC))

@@

```{r LIVARR08-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # LIVARR08: Living arrangement of respondent’s household (8 categories)
    LIVARR08 = 
           case_when(LIVARR08 == 1 ~ "Under 25 years - Not living with parents",
                     LIVARR08 == 2 ~ "Under 25 years - Living with both parents",
                     LIVARR08 == 3 ~ "Under 25 years - Living with mother only",
                     LIVARR08 == 4 ~ "Under 25 years - Living with father only",
                     LIVARR08 == 5 ~ "25 years of age or older - Not living with parents",
                     LIVARR08 == 6 ~ "25 years of age or older - Living with both parents",
                     LIVARR08 == 7 ~ "25 years of age or older - Living with mother only",
                     LIVARR08 == 8 ~ "25 years of age or older - Living with father only"), 
    LIVARR08 = factor(LIVARR08))

@@

```{r HSDSIZEC-2010}
values_ordered <- c("One person household",
                   "Two person household",
                   "Three person household",
                   "Four person household",
                   "Five person household",
                   "Six or more person household")

@@

```{r HSDELIGC-2010}
values_ordered <- c("One member",
                     "Two members",
                     "Three members",
                     "Four members", "Five household members or more")

@@

summary(gss_main_2010$HSDELIGC)
```

```{r FAMTYPE-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # FAMTYPE: Respondent's type of family structure.
    FAMTYPE = 
           case_when(FAMTYPE == 1 ~ "Couple only", 
                     FAMTYPE == 2 ~ "Intact family",
                     FAMTYPE == 3 ~ "Step family with common child",
                     FAMTYPE == 4 ~ "Step family without a common child",
                     FAMTYPE == 5 ~ "Lone parent family",
                     FAMTYPE == 7 ~ "No spouse/partner or children in household"), 
    FAMTYPE = factor(FAMTYPE))

@@

```{r MULTIGEN-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # MULTIGEN:  Three generations or more in the respondent’s household
    MULTIGEN = 
           case_when(MULTIGEN == 1 ~ "Yes", 
                     MULTIGEN == 2 ~ "No",
                     MULTIGEN == 6 ~ "Number of generations unknown"), 
    MULTIGEN = factor(MULTIGEN))

@@

summary(gss_main_2010$PRV) 
```

```{r REGION-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # REGION:  Region of residence of the respondent.
    REGION = 
      case_when(REGION == 1 ~ "Atlantic region",
                     REGION == 2 ~ "Quebec",
                     REGION == 3 ~ "Ontario",
                     REGION == 4 ~ "Prairie region",
                     REGION == 5 ~ "British Columbia"),
    REGION = factor(REGION))

@@

```{r LUC_RST-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # LUC_RST:  Population centre indicator
    LUC_RST = 
      case_when(LUC_RST == 1 ~ "CMA/CA",
                     LUC_RST == 2 ~ "non CMA/CA",
                     LUC_RST == 3 ~ "Prince Edward Island"),
    LUC_RST = factor(LUC_RST))

@@

```{r GTU_110-2010}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r GTU_130-2010}
values_ordered <- c("Every day",
                    "A few times a week",
                    "About once a week",
                    "About once a month",
                    "Less than once a month",
                    "Never", 
                    "Don't know")

@@

```{r DVTDAY-2010}
gss_main_2010 <- gss_main_2010 %>% 
  mutate( # DVTDAY: Diary - Reference day - Type
    DVTDAY = 
      case_when(DVTDAY == 1 ~ "Weekday",
                     DVTDAY == 2 ~ "Saturday",
                     DVTDAY == 3 ~ "Sunday"),
    DVTDAY = factor(DVTDAY))

@@

Save data in R format for later use:
```{r save-data-2010}
usethis::use_data(gss_main_2010, 
                  overwrite = TRUE)
```

@@

```{r filtering-variables-22005015}
gss_main_2005 <- gss_m_2005 %>%
  select(RECID:DVTDAY)
```

@@

Read the Main files of the 1998 GSS survey:

@@

Read the Main files of the 1992 GSS survey:
